\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Paper Précis: Creating a Shared Understanding of Testing Culture on a Social Coding Site}

### 2014-11-20 article_2.tex
Completed 'Study Design'

We used an approach based on Grounded Theory (GT) [7] to explore how testing is carried out on social coding sites and how an increased social transparency impacts the testing behavior of software developers engaged in those projects. For the purposes of this paper, we focused on two groups. of people: (1) project owners, who receive pull requests and (2) contributors who send them.

@@

We designed a set of research questions to better understand how testing practices evolve based on the interaction between contributors and project owners on social coding sites. First, we focused on identifying the main steps and variations of the contribution process and how decisions are made with regard to testing. This leads to our first research question:
RQ1: What is the contribution process with regard to testing on social coding sites?
While investigating the contribution process on GitHub, it became clear that contributions were assessed by project owners. Furthermore, we found different motivations for im- plementing quality assurance measures specific to interaction on social coding sites. We refined our first research question into two sub questions to accommodate this.
RQ1.1: How do project owners assess incoming contribu- tions from contributors?
RQ1.2: What are the internal and external motivations for engaging in testing efforts on social coding sites?
As reported by Stuart et al. [5], social transparency may have hard to anticipate second order effects in addition to the possibly intended first order effects. In our study, we wanted to find out more about the issues that might arise as a result of those effects. As such, our second research question is:
RQ2: What challenges and risks related to testing arise from engaging in projects on social coding sites?
In face of such challenges and risks, project owners and contributors might have to evolve and adapt their contribution process. For example, project owners might have to advise contributors on how to conform to project guidelines. Our third research question focuses on the actions taken by each group of actors for overcoming such issues:
RQ3: How do developers cope with those challenges and risks related to testing?
Finally, the increased social transparency on social coding sites creates distinct modes of interaction between project collaborators. Understanding these modes of interaction can help guiding practitioners as to which kind of interactions to support and which to avoid in the purpose of improving the existing testing practices. This leads to our last research question:
RQ4: What impact does the participation on social coding projects have on testing practices?

@@

Grounded Theory [7] emphasizes a continuous data collec- tion process interlaced with periodic pauses for analysis. As such, we conducted our study in three phases.
First, we focused on understanding which testing-related norms and conventions exist on GitHub. For our investigation, we obtained 16,000 email addresses of recently active users
by querying the GitHub Archive3. From this pool, we invited 50 users to semi-structured interviews and another 50 users by randomly choosing a member from each of the 50 most successful GitHub teams as listed on the Coderwall4 leader- board. This sampling strategy resulted in a diverse population: highly experienced as well as regular users of GitHub.
Of these 100 users, 10 from the former sample and 3 from the latter sample enrolled. Each participant was interviewed by a member of our research team via voice call. Interviews lasted approximately 20 minutes and the audio was recorded. We asked the participants to outline the testing process in one of their public projects on GitHub. Preliminary findings indi- cated that projects featuring extensive collaboration between developers would demand more elaborate testing approaches. We also learned that most decisions regarding testing were made when pull requests were sent and received, i.e., when people had to coordinate and negotiate their cooperation.
In the second phase of our research, we defined our target population to be active users who used the collaboration features of GitHub. From our address pool, we invited 1,000 GitHub users at random to take our first questionnaire (Q1): 500 at first and again 500 after 6 days. In total, 158 users responded, of which 74 left usable contact information. The questionnaire responses allowed us to distinguish between users that had been collaboratively active ? they had either sent a pull request or forked a project ? and their approaches for testing contributions. We invited all 62 of those 74 who matched our criteria for another round of semi-structured interviews. 20 users enrolled.
In these interviews, we inquired about participants? testing practices and values. We had prior answers to these questions from questionnaire Q1 and used the interviews to explore such situations in detail, allowing us to better understand the contribution process with a focus on testing behavior and practices. For example, we asked interviewees how they handled incoming pull requests and whether they had any kind of quality assurance measures related to this process. Then, we inquired about their motivations for assuring quality and the challenges they face when contributing to other projects. As a result of our second phase, we were able to identify five themes that stood out.
1) The fork and pull request mechanisms, social network features, and integration of numerous tools result in a GitHub-specific process for sending and receiving contributions.
2) GitHub makes it easier to access a public repository, start working on it, handle contributions, and discuss them with contributors. GitHub tools and social features lower the barriers for engagement in software projects.
3) Public projects and profiles on GitHub have high expo- sure to many potential contributors and users. This helps with, for example, discovering edge cases.
4) GitHub integrates many tools into the project context and centralizes many interactions and notifications
among project participants.
5) GitHub provides increased social transparency that al-
lows its users to see the identity, actions, and com- munications between users, a phenomenon that was previously reported on by Dabbish et al. [3].
In the last phase, a final questionnaire (Q2) was sent to 4,000 random GitHub users for quantitative validation of our findings. Of these users, 569 responded. The results of this phase can be found in section VI

\subsection{Data Analysis}

We alternated periods of data collection with analysis in order to build up our theory. At the end of each data collection phase, we transcribed the recorded interviews and open coded them. This resulted in 172 codes. At the end of our second phase, we engaged in axial coding our codes in order to find higher level conceptual themes that would help us in answering our research questions. In the last phase of our research, core themes of our theory were formed into statements and validated through a final questionnaire (cf. section VI). Partic- ipants were asked to agree or disagree with statements using a Likert-type scale. For each question, the mean value for the given set of answers was calculated, as well as its variance and the number of given answers to that question in total. For questions that required the participant to choose an answer in a set of pre-given answers, the count for each answer was calculated and related to the total number of answers to that question.

\subsection{Participants}

Overall, we interviewed 33 people, among them software developers, testers, and software architects. Nearly half of them were using GitHub for professional work (19); the other half (14) used GitHub for private projects. Our population comprised of developers employed in a software company (24), self-employed (3), and unemployed developers (2). 4 in- terviewees were affiliated with universities and mostly engaged in noncommercial projects. 20 participants of our second interview phase estimated the number of total contributors to their projects. Numbers of contributors were diverse: 12 projects with up to ten contributors, two projects with up to one hundred contributors and six projects with over one hundred contributors. We denote these interviewees with FI. Randomly chosen interviewees from the first interview round are denoted with R, Coderwall leaderboard members are denoted with L.

@@

>>>>

Our basing paper employs a general research method, Grounded Theory \citep{Anselm}, to explore how testing is carried out on GitHub and investigate how increased social transparency influences testing behaviour. 
Pham emphasised on two groups of people:
\begin{enumerate}
	\item project owners, who receive pull requests
	\item contributors who send them
\end{enumerate}

@@

For the initial data collection phase a survey was designed which included five questions to better help "understand how testing practices evolve based on the interaction between contributors and project owners on social coding sites" \citep{Pham}. This questionnaire (Q1) analysed the following topics:
\begin{itemize}
	\item how project owners assess incoming contributions
	\item internal and external motivations for engaging in testing efforts
	\item the challenges and risks related to testing
	\item how developers code with those challenges and risks
	\item	the impact of participating on social coding projects has on testing practices
\end{itemize}

@@

Grounded Theory \citep{Anselm} involves continuous data collection accompanied with periodic pauses for analysis. Accordingly, our basing study was conducted in three incremental phases of analysis. Pham first enlisted a diverse sample population though inviting active GitHub users belonging to popular OSS projects and random recently active GitHubs users. The first phase sought to understand which testing-related norms and conventions exist on Github through broadly asking participants to outline their testing process in one of their public projects. The findings from this phase posed that projects which featured extensive collaboration between developers would demand more elaborate testing approaches. Additionally, these findings indicated that most decisions regarding testing were made when pull requests were sent and received, hence when people had to coordinate and negotiate their cooperation.
\par
Subsequently, the second phase of the analysis involved refining the target population to be "active users who used the collaboration features of GitHub" \citep{Pham}. Such was achieved by inviting the sample pool to take the first questionnaire (Q1), whereby the questionnaire responses made it possible to distinguish those users that had been collaboratively active and their approaches from testing contributions. Furthering from this, the refined target population were invited to a round of semi-structured interviews exploring participant's testing practices and values. Several common themes emerged from interviews:

\begin{enumerate}
	\item The social network features, fork and pull request mechanisms, and integration of numerous tools result 		in a GitHub-specific process for sending and receiving contributions.
	\item GitHub tools and social features lower the barriers for engagement in software projects.
	\item GitHub integrates many tools into the project context and centralizes many interactions and notifications
		among project participants.
	\item GitHub provides increased social transparency that al-
		lows its users to see the identity, actions, and com- munications between users
\end{enumerate}

In the last phase, a final questionnaire (Q2) was sent to random GitHub users for quantitative validation of Pham's findings, this is outlined in section V.

@@

\section{Validating Findings}

In section V, we presented findings gathered by conducting 33 interviews with GitHub users. This section presents the most striking results of our final questionnaire (Q2) that we used to validate core statements of our findings. Of 4,000 random GitHub users, 569 filled out this questionnaire. Our results are summarized in Table I. PO denotes statements about project owners, C about contributors. For each question, we presented the participant with a Likert scale of five items ranging from ?I do not agree at all? to ?I strongly agree.?. These Likert items are represented in the diagrams on the X- axis with disagreement being on the left and agreement being on the right hand-side. The middle bar represents the neutral item. The number of answers accumulated for each Likert item is marked on the Y-axis. The grey bar is the median.
The questionnaire required the participant to take both the perspective of a project owner and a contributor. 39\% of our participants would receive pull requests at least a few times per week (daily: 16\%) and 27\% send pull requests at least a few times per week (daily: 6\%). Even though several interviewees mentioned voluntarism as a hindering factor, the questionnaire did not validate this (PO1). Personal traits such as modesty and humility of the requester as well as value given to the contribution may be influencing factors. Similarly, most of the participants did not agree to feel a need for automation (PO2). However, as some interviewees mentioned, this need may depend on the size and popularity of the project in question. As popularity grows, the amount of incoming pull requests increases. As both samples were randomly invited, but ultimately self-selected, variations in populations might attribute for this dissonance.
Project owners agree that providing tests in one?s project lowers the support effort regarding testing by contributors (PO3). Appropriately, contributors heavily rely on existing test cases when creating their own. They use these to learn how testing is done in a specific project (C3) and, lastly, even copy existing tests and use them as a basis for new tests (C4). With tests in place, contributors feel obligated to add their own tests and seem to comply with this implicit demand (C2).
